Analyzing Students Use Metacognitive Strategies When Interacting with GenAI-Powered Chatbots in Programming Courses.

### 2025-01-27 ETHE/sn-article.tex
ETHE update

\author*[1,2]{\fnm{Rodrigo} \sur{Prestes Machado}}\email{rodrigo.prestes@poa.ifrs.edu.br}

\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}

\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}

>>>>

\author*[1]{\fnm{Rodrigo} \sur{Prestes Machado}}\email{rodrigo.prestes@poa.ifrs.edu.br}
\author*[2]{\fnm{Carlos} \sur{Alario-Hoyos}}\email{calario@it.uc3m.es}
\author[2]{\fnm{Iria} \sur{Estévez-Ayres}}\email{ayres@it.uc3m.es}
\author[2]{\fnm{Patricia} \sur{Callejo}}\email{pcallejo@it.uc3m.es}
\author[2]{\fnm{Carlos} \sur{Delgado Kloos}}\email{cdk@it.uc3m.es}

\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Informatics}, \orgname{Federal Institute of Education,
Science and Technology}, \orgaddress{\street{Cel. Vicente}, \city{Porto Alegre},
\postcode{90.030-041}, \state{Rio Grande do Sul}, \country{Brazil}}}

\affil[2]{\orgdiv{Department of Telematics Engineering},
\orgname{Universidad Carlos III}, \orgaddress{ \street{Av. de la Universidad},
\city{Leganés}, \postcode{28911}, \state{Madrid}, \country{Spain}}}
